Analysis paper

### 2021-04-22 analysis/analysis.Rmd
update analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(covid.german.forecasts)
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(patchwork)

# load and set up data
cases <- combined_data[target_type == "case" & 
                         as.Date(forecast_date) %in% forecast_dates$cases]
deaths <- combined_data[target_type == "death" & 
                         as.Date(forecast_date) %in% forecast_dates$deaths]
data <- rbindlist(list(cases, deaths))
```

## Visualisation of data

```{r fig.height=10, fig.width=15}
df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
                      grepl("2", target) & 
                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]

truth <- dcast(df, ... ~ quantile, value.var = "prediction")[
  , .(location_name, target_end_date, target_type, true_value)] %>%
  unique()

truth <- truth[order(location_name, target_type, target_end_date)]

epi_classification <- function(actual_value, first_diff, threshold = 0.05) {
  out <- ifelse(first_diff > 0, "rising", "falling")
  out[abs(first_diff) < 0.05 * actual_value] <- "stable"
  return(out)
}

truth[, first_diff := c(NA, diff(true_value)), 
      by = c("location_name", "target_type")]
truth[, epi_class := epi_classification(true_value, first_diff), 
      by = c("location_name", "target_type")]
truth[, shift_date := shift(target_end_date, -1), 
      by = c("location_name", "target_type")]
# truth[, second_diff := c(NA, diff(first_diff)), 
#       by = c("location_name", "target_type")]

ggplot(truth, aes(x = target_end_date)) + 
  geom_rect(aes(xmin = target_end_date, xmax = shift_date, ymin = -Inf, ymax = Inf, fill = factor(epi_class)), alpha = 0.2) +
  geom_line(aes(y = true_value, color = "truth")) + 
  geom_line(aes(y = first_diff, color = "first diff")) +
  labs(y = "value", x = "date") + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom")

@@

## Visualisation of forecasts and scores

This includes all available dates for the forecast plot. For the score plot it includes the full set for cases, and a restricted set for deaths. The restricted set is all forecasts from "2020-12-07" on to make sure that we have a full set of forecasts for deaths. The plot also includes the Christmas period - it probably makes sense to gray that out.

```{r fig.height=10, fig.width=15}
df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
                      grepl("2", target) & 
                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]

@@

truth_vs_forecast_2 <- df %>%
  ggplot(aes(y = true_value, x = target_end_date, colour = model, fill = model)) + 
  geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
                 size = 1.5,
                 alpha = 0.4,
                 position = position_dodge(width = 3)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.5,
                 alpha = 0.8,
                 position = position_dodge(width = 3)) + 
  labs(y = "value", x = "date") + 
  geom_point() + 
  geom_line() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom")

@@

```{r fig.height=10, fig.width=15}
# plot with scores over time ---------------------------------------------------
scores_target_forecastdate <- eval_forecasts(
  data = data[grepl("2", target)],
  summarise_by = c("model", "location_name", "target_type", "forecast_date"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

wis_scores_time_2 <- scores_target_forecastdate  %>%
  ggplot(aes(x = as.Date(forecast_date), y = interval_score, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") +
  theme(legend.position = "bottom") +
  labs(y = "weighted interval score", x = "date")

ggsave(here("analysis", "plots", "wis-over-time.png"), 
       plot = wis_scores_time_2)
```

```{r}
### same plot with mean score ratio
rel_skill_time_2 <- scores_target_forecastdate  %>%
  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, fill = model, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") +
  theme(legend.position = "bottom") +
  labs(y = "relative skill", x = "date")

ggsave(here("analysis", "plots", "wis-over-time.png"), 
       plot = rel_skill_time_2)
```

```{r fig.height=16, fig.width=8}
# glue two plots together
truth_vs_forecast_2 / rel_skill_time_2 + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom') 
ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
```

@@

- severe overshooting for Renewal model
- all models are terrible around Christmas
- the artifacts around Christmas hit Renewal hardest
- the Christmas effect is much stronger in Germany than in Poland
- need to increase value for position dodge
- reporting artifacts around christmas

- [ ] shade dates that are excluded in "official scoring"
- [ ] maybe add density plot with scores on the y axis
- [ ] remove baseline from relative skill plot
- [ ] make both plots nicer
    - [ ] increase dodge
    - [ ] change colour scheme
    - [ ] adjust size of points
- [ ] presumably change how plots are arranged
- [ ] make final decision whether we want to have relative skill or just WIS on the other plot
    - WIS would show the overall level (which scales with the number of cases)
    - relative skill corrects for that in some sene, but also introduces other biases

**Further things we could look at**

- maybe look at correlation between the number of weekly cases and the score?
- look at scores for rising and falling parts of the epidemic separately
- maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?"

@@

This excludes all forecasts made on c("2020-12-21", "2020-12-28").

```{r}
# create helper function to make table
make_score_table <- function(scores) {
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("target_type", "interval_score", "aem", "relative_skill", "scaled_rel_skill"), 
           new = c("target", "WIS", "absolute error", "rel. skill", "scaled rel. skill"))

  table <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")][
    order(target, `scaled rel. skill`)
  ] %>%
    kable(format = "markdown")
  return(table)
}
```

@@

coverage <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "range"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[range %in% c(50, 90), 
                   .(model, target_type, coverage, range)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")
setnames(coverage, old = c("50", "90"), new = c("coverage 50%", "coverage 90%"))

@@

### 4 weeks ahead
```{r }
# scores by target type for 4 week ahead forecasts
coverage <- eval_forecasts(
  data[grepl("4", target)], 
  summarise_by = c("model", "target_type", "range"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[range %in% c(50, 90), 
                   .(model, target_type, coverage, range)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")
setnames(coverage, old = c("50", "90"), new = c("coverage 50%", "coverage 90%"))

eval_forecasts(
  data[grepl("4", target)], 
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "target_type")) %>%
  make_score_table()

@@

**To do**
- [] make a final decision (and document it somewhere) about how we want to exclude the Christmas period. Right now we are excluding forecast dates, but do not restrict target end dates in any way.

**Further things to look at**
- maybe think about some kind of stratification by time?

@@

## Look more closely at relative skill

--> not sure what we wanted to do here.

@@

## Analyse distribution of model rankings

```{r }
# scores by target type for 4 week ahead forecasts
scores <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "location_name", "forecast_date")
)

ranked_scores <- scores %>%
  dplyr::mutate(forecast_date = as.Date(forecast_date)) %>%
  dplyr::group_by(forecast_date, location_name, target_type) %>%
  dplyr::mutate(num_forecasts = dplyr::n(), 
                rank = rank(interval_score, ties.method = "average",
                                           na.last = NA), 
                standard_rank = round((1 - (rank - 1) / (num_forecasts - 1)) * 100)) %>%
  dplyr::ungroup()

setDT(ranked_scores)
df <- ranked_scores[, .(rank_count = .N), 
                    by = c("target_type", "location_name", "model", "rank")][, 
                      sum := .N, by = c("target_type", "location_name")
                    ][, rank_count := rank_count / sum]

ggplot(df, aes(y = model, x = rank, 
                          group = model, fill = model)) + 
  ggridges::geom_ridgeline(aes(height = rank_count)) + 
  facet_wrap(location_name ~ target_type, scales = "free_x")

ggplot(ranked_scores, aes(y = model, x = rank, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges(stat = "binline") + 
  facet_wrap(location_name ~ target_type, scales = "free_x")

@@

**what we learn from this plot**

- bimodal distribution is interesting

**To do**

- [ ] make plot nicer
- [ ] maybe make this with relative skill instead
- [ ] finish this todo list
- [ ] maybe a density plot instead of a ridge plot?

@@

## Look at WIS contributions
```{r}
scores_target <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE
)

wis_components(scores_target, 
               facet_formula = ~ target_type, 
               scales = "free_x", 
               relative_contributions = TRUE,
               x_text_angle = 0) + 
  theme(legend.position = "bottom") + 
  coord_flip() + 
  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
       x = NULL)

scores_target <- eval_forecasts(
  data[grepl("4", target)], 
  summarise_by = c("model", "location_name", "target_type"), 
  compute_relative_skill = TRUE
)

wis_components(scores_target, 
               facet_formula = location_name ~ target_type, 
               facet_wrap_or_grid = "grid",
               scales = "free_x", 
               x_text_angle = 0) + 
  theme(legend.position = "bottom") + 
  coord_flip() + 
  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
       x = NULL)

- [ ] have the second plot stratified by epidemic period

## Look more closely at interventions and change points

- one interesting point Johannes brought up is that scoring predictions aroud change points may not even be such a good idea. The reason is that if you have a modle that always predicts a change point, theat model will do very well according to this metric even if it doesn't add much value. For example, we would expect the baseline model to do very well according to this change point metric

## Look at the effect of data exclusions

@@

## Look more closely at calibration and sharpness

```{r, eval = TRUE}
scores_target <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "range", "quantile"), 
  compute_relative_skill = FALSE
)

interval_coverage(scores_target, 
                  facet_formula = ~ target_type)

scores_target <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "location_name", "target_type", "range", "quantile"), 
  compute_relative_skill = FALSE
)

interval_coverage(scores_target, 
                  facet_formula = location_name ~ target_type, 
                  facet_wrap_or_grid = "grid")

- models are widely overconfident in their predictive ability
- more overconfidence with cases than deaths

- maybe make tihs a PIT plot
- stratify by period

## Look at scores based on log predictions and log truth values
```{r, eval = TRUE}

log_data <- copy(data)[, `:=`(true_value = log(true_value), 
                              prediction = log(prediction))]

### Table 2 weeks ahead
```{r, eval = TRUE}
log_scores_target_2 <- eval_forecasts(
  log_data[grepl("2", target)], 
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

log_scores_target_2 %>%
  make_score_table()
```

### Table 2 weeks ahead
```{r, eval = TRUE}
log_scores_target_4 <- eval_forecasts(
  log_data[grepl("4", target)], 
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

log_scores_target_4 %>%
  make_score_table()
```

**What we learn**
- results and rankings change if we look at scores of log values
- this makes sense as presumably outliers aren't punished so harshly (inconsistent? models with large outliers are treated more leniently)

### scores for logged values over time
```{r, eval = TRUE}
log_scores_target_forecast_date_2 <- eval_forecasts(
  log_data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "forecast_date", "location_name"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

rel_skill_time_2 <- log_scores_target_forecast_date_2  %>%
  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") +
  theme(legend.position = "bottom") +
  labs(y = "relative skill", x = "date")

rel_skill_time_2
```

**what we learn**
- nothing? 
- it looks slightly different, but similar and also similarly confusing

### WIS components for scores of logged values
```{r, eval = TRUE}
log_scores_target_location_2 <- eval_forecasts(
  log_data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "location_name"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

wis_components(log_scores_target_location_2, 
               facet_formula = location_name ~ target_type, 
               facet_wrap_or_grid = "grid",
               scales = "free_x", 
               x_text_angle = 0) + 
  theme(legend.position = "bottom") + 
  coord_flip() + 
  labs(title = "Components of the weighted interval score for 2-week ahead forecasts", 
       x = NULL) 
```
**what we learn**

- the Renewal model benefits from this scoring scheme (except for Polish deaths)
- interesting (confusing?) that the Baseline model is now the worst model for Polish cases. What's the mechanism behind that? is it just bad on average, but has no outliers?

**To do**

- at least for me (Nikos): get an intuition for what actually changes when you look at scores of logged predictions and what does it imply. What kind of model benefits from one or the other evaluation scheme?

Thoughts about what changes when you look at logged predictions

- models with outliers benefit
- do models lose out that aren't great, but have no outliers?

## Further interesting things

- look at crowd performance as a function of the number of forecasts --> maybe leave that to a second paper

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(covid.german.forecasts)
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
```

```{r helper-functions}
# classify epidemic according to whether, on a given forecast date, the two
# weeks before that have seen monotonic rise, decline, or an unclear trend
classify_epidemic <- function(data, cutoff = 0.05, growth_cutoff = 2) {
  dt <- as.data.table(data)

  # calculate differences and set differences smaller than 
  # a certain cutoff to zero
  dt[, diff_1 := c(NA, diff(true_value, 1)), 
     by = c("location_name", "target_type")]
  dt[abs(diff_1) < (cutoff * true_value), diff_1 := 0]
  dt[, diff_prev := c(shift(diff_1, 1)), 
     by = c("location_name", "target_type")]

  # assign a label depending on observed differences
  dt[, c("classification", "speed") := "unclear"]
  dt[(diff_1 >= 0 & diff_prev >= 0), 
     classification := "increasing"]
  dt[(diff_1 <= 0 & diff_prev <= 0 ), 
     classification := "decreasing"]
  dt[(diff_1 == 0 & diff_prev == 0), 
     classification := "unclear"]
  dt[(classification == "increasing") & 
       diff_1 > growth_cutoff * diff_prev, 
     speed := "accelerating"]
    dt[(classification == "increasing") & 
         diff_1 < 1/growth_cutoff * diff_prev, 
     speed := "decelerating"]
  dt[(classification == "decreasing") & 
       abs(diff_1) > growth_cutoff * abs(diff_prev), 
     speed := "accelerating"]
  dt[(classification == "decreasing") & 
       abs(diff_1) < 1/growth_cutoff * abs(diff_prev), 
     speed := "decelerating"]

  dt[, c("diff_1", "diff_prev") := NULL]
  return(dt)
}

@@

```{r}
# load and set up data
cases <- combined_data[target_type == "case" & 
                         as.Date(forecast_date) %in% forecast_dates$cases]
deaths <- combined_data[target_type == "death" & 
                         as.Date(forecast_date) %in% forecast_dates$deaths]
data <- rbindlist(list(cases, deaths))
data[, location_target := paste0(target_type, "s", " in ", location_name)]

# obtain classification
epitrend <- classify_epidemic(truth_data)
epitrend[, forecast_date := target_end_date + 2]
epitrend[, true_value := NULL]

## Todo

- [ ] final decision on the Christmas period. Do we want to also exclude target end dates, or just forceast dates? Do we want to exclude the 2nd of January?
- [ ] look more closely into the stratification: do we want the current thing or do we want something else that has the outcome in it as well? One thing I thought was have another category: inflection or no inflection and also score that?
- [ ] Talk to Johannes about whether we want to score log forecasts and log truth values instead. I for now removed that part for the following reasons: I currently don't have a good feeling for what it does. I'm somewhat hesitant that establishing a completely new way of scoring forecasts could be beyond the scope of this paper. Very happy to switch to it entirely if we agree it is the better metric, but not sure we are at that point yet.

## Visualisation of 2 week ahead forecasts and scores

```{r truth-vs-forecasts, fig.height=10, fig.width=15}
# load unfiltered combined data 
df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
                      grepl("2", target) & 
                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
df[, location_target := paste0(target_type, "s", " in ", location_name)]

@@

# add trend classification
df <- merge(df, epitrend, 
            by = c("target_end_date", "location_name", "target_type"))

truth_vs_forecast_2 <- df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
  #                size = 1.5,
  #                alpha = 0.4,
  #                position = position_dodge(width = 3)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.5,
                 alpha = 1,
                 position = position_dodge(width = 6)) + 
  labs(y = "value", x = "date") + 
  geom_point(aes(shape = classification)) + 
  geom_line() + 
  geom_rect(aes(xmin = min(forecast_dates$christmas) + 14, # 2wk ahead forecast
                xmax = max(forecast_dates$christmas) + 14,
                ymin = -Inf,
                ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  theme_light() + 
  facet_wrap(~ location_target, scales = "free", ncol = 1) + 
  theme(legend.position = "bottom") + 
  scale_color_brewer(palette = "Accent") + 
  theme(panel.background = element_rect(fill = "#e1f0fe"))

@@

```{r scores-over-time, fig.height=10, fig.width=15}
# plot with scores over time ---------------------------------------------------
scores_target_forecastdate <- eval_forecasts(
  data = data[grepl("2", target)],
  summarise_by = c("model", "location_name", "target_type", "forecast_date", "location_target"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

# add epi trend classification
scores_target_forecastdate[, forecast_date := as.Date(forecast_date)]
scores_target_forecastdate <-  merge(scores_target_forecastdate, epitrend, 
            by = c("forecast_date", "location_name", "target_type"))

rel_skill_time_2 <- scores_target_forecastdate  %>%
  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill)) + 
  geom_line(aes(colour = model)) + 
  geom_point(aes(shape = classification, colour = model)) + 
  theme_light() + 
  facet_wrap( ~ location_target, ncol = 1, scales = "free_y") +
  theme(legend.position = "bottom") +
  labs(y = "relative skill", x = "date") + 
  geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
                xmax = max(forecast_dates$christmas) + 14,
                ymin = 0,
                ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  scale_color_brewer(palette = "Accent") + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_y_log10()

ggsave(here("analysis", "plots", "rel-skill-over-time.png"), 
       plot = rel_skill_time_2)
```

```{r fig.height=10, fig.width=15}
# glue two plots together
truth_vs_forecast_2 | rel_skill_time_2 + 
  plot_layout(guides = "collect") & 
  theme(legend.position = 'bottom') 
ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
```
*Figure 1. Left: Visualisation of 2 week ahead forecasts against the true observed values. The shape indicates whether there has been a monotonic increase or decrease over the last two weeks, or an unclear trend. Forecasts made during the Christmas period (from 2020-12-19 until 2021-01-02) are grayed out. Right: Corresponding scaled relative skill scores for the forecasts shown on the left. Scaled relative skill scores can be thought of as 'improvement over the baseline model' (see Methods for details).*

@@

- severe overshooting for Renewal model
- all models are terrible around Christmas
- the artifacts around Christmas hit Renewal hardest
- the Christmas effect is much stronger in Germany than in Poland

**Todo**
- [ ] maybe remove baseline from relative skill plot
- [ ] maybe rearrange plots
- [ ] make plots nicer (legend, maybe point size on the left / remove either points or lines)

@@

```{r}
# create helper function to make table
make_score_table <- function(scores) {
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("model", "target_type", "interval_score", "aem", 
                   "relative_skill", "scaled_rel_skill", "sharpness", 
                   "underprediction", "overprediction", "bias", 
                   "50", "90"), 
           new = c("Model", "Target", "WIS", "Abs. error", 
                   "rel. skill", "Skill", "Sharpness", 
                   "Underpred.", "Overpred.", "Bias", 
                   "50%-Cov.", "90%-Cov."))

  scores <- scores[, lapply(.SD, FUN = function(x) {
    if (is.numeric(x)) {
      return(round(signif(x, 3), 2))
    } else {
      return(x)
    }
  })]

  scores <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")][
    order(Target, `Skill`)
  ]

  setcolorder(scores, 
              neworder = c("Model", "Target", "Skill"))

  # add an empty line to data.frame to separate deaths and cases
  table <- 
    rbindlist(list(
    scores[1:4], 
    as.list(rep(NA, ncol(scores))), 
    scores[5:9]
  )) %>%
    kable(format = "markdown") %>%
    kable_styling(bootstrap_options = "striped")
  return(table)
}
```

@@

coverage <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "range"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[range %in% c(50, 90), 
                   .(model, target_type, coverage, range)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")

@@

*Table 1: Scores for 2 week ahead forecasts (excluding the 21st and 28th of December 2020, cut to three significant digits and rounded). Skill is the scaled relative skill, a measure of relative performance with respect to the baseline model. Sharpness, overprediction and underprediction together some up to the weighted interval score (WIS). Bias (between -1 and 1) represents the general average tendency of a model to over- or underpredict. 50% and 90%-coverage are the percentage of observed values that fell within the 50% and 90% prediction intervals of a model.*

## Analyse distribution of scores

```{r}
# scores by target type for 4 week ahead forecasts
scores <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "location_name", "forecast_date", 
                   "location_target"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[model != "Baseline"]

scores[, forecast_date := as.Date(forecast_date)]
scores <-  merge(scores, epitrend, 
            by = c("forecast_date", "location_name", "target_type"))

@@

```{r}
p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_brewer(palette = "Accent") + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ location_target) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

```{r}
# scores for different phases of the epidemic
scores[, target_phase := paste0(target_type, "s - ", classification, " phase")]
p_phases <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_brewer(palette = "Accent") + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ target_phase) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

```{r fig.height=10, fig.width=15}

p / p_phases + 
  plot_layout(guides = "collect") & 
  theme(legend.position = 'bottom')

*Figure 2. Top: Distribution of the scaled relative skill scores for the different model and forecast targets. The vertical black line represents the baseline model. Models beat the baseline more easily for death forecasts. The renewal model had by far the most variance in terms of its performance, while the crowd forecasting model seems most consistent. Bottom: Distribution of scaled relative skill in different phases of the epidemic. The epidemic was classified as 'increasing', if the forecast point and the two data points before form a monotonically rising line, 'decreasing' if numbers were falling and 'unclear' otherwise. This plot seems like a lot of noise to me, but unsure.*

@@

## WIS contributions
```{r}
df <- data[grepl("2", target)] %>%
  merge(epitrend, 
        by = c("target_end_date", "location_name", "target_type"))

scores_target <- eval_forecasts(
  df, 
  summarise_by = c("model", "target_type", "classification"), 
  compute_relative_skill = TRUE
)

scores_target[, target_phase := paste0(target_type, "s - ", 
                                       classification, " phase")]

wis_components(scores_target, 
               facet_formula = ~ target_phase, 
               scales = "free_x", 
               relative_contributions = TRUE,
               x_text_angle = 0) + 
  theme(legend.position = "bottom") + 
  coord_flip() + 
  labs(x = NULL)

*Figure 3. Relative contributions of sharpness, overprediction and underprediction to the weighted interval scores. Models overpredict in a decreasing phase and underpredict in a decreasing phase. So far so obvious. Somehow adding inflection points would be really cool - maybe stratify according to "decreasing, but inflection afterwards etc.?". Apparently the baseline model is really good in an unclear phase, just much too uncertain?.*

@@

## Calibration

```{r, eval = TRUE}
df <- data[grepl("2", target)] %>%
  merge(epitrend, 
        by = c("target_end_date", "location_name", "target_type"))

scores_target <- eval_forecasts(
  df, 
  summarise_by = c("model", "target_type", "classification", "range", "quantile"), 
  compute_relative_skill = FALSE, 
  pit_plots = TRUE
)

interval_coverage(scores_target, 
                  facet_formula = ~ target_type + classification)

@@

  *Figure 4: Comparison of nominal and empirical coverage (percentage of true observed values covered by a given prediction interval). The one thing I find interesting about this plot is that models are apparently much too confident when there is an increasing trend. I feel this is probably actionable advice (even though it could probably be made better using a separate analysis about optimal uncertainty that is beyond the scope of this paper). *

- maybe make this a PIT plot

@@

## Supplementary Material

### Look at the effect of data exclusions

@@

<!-- **Further things we could look at** -->

<!-- - maybe look at correlation between the number of weekly cases and the score? -->
<!-- - maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?" -->
<!-- - look at crowd performance as a function of the number of forecasts --> maybe leave that to a second paper -->
